Leadership across cultures and contexts: an exploratory analysis

### 2020-04-30 leadership_across_cultures_contexts.Rmd

<!-- INTRO TO MOTIVATE PAPER -->
Research on leadership within anthropology extends to the birth of the discipline. Early on, anthropologists (and some sociologists) realized that leadership and followership were critical to understanding human psychology, social organization, and culture [e.g., @mumford_origins_1906; @firth1927economic; @morgan_ancient_1877; @myres_influence_1917]. Anthropologists documented some sort of leadership among every ethnographically observed society [@brown_human_1991; @lewis_leaders_1974], and across many social contexts, such as families and kin groups [@dussart2000politics], ritual [@singh_cultural_2017], work groups [@macfarlan_competitive_2012], conflicts between groups [@glowacki_evolutionary_2017], and in nonindustrial political groups [@cohen_comparative_1967]. For review, see @garfield_review_2019.

@@

Since the seminal WEIRD people paper, many social scientists have indeed taken up the challenge to diversify their samples and have sought out "non-WEIRD" participants and databases. Dichotomizing populations and their psychologies and social dynamics as WEIRD or non-WEIRD, however, is a mistake.^[A Google Scholar search for "non-WEIRD" produced over 1000 results.] Anthropology, on the other hand, has been criticized for exoticizing and essentializing the "Other" [@said1979; @abu2008]. @abu2008 [p. 470], for instance, notes that

@@

>>>>

<!-- INTRO TO MOTIVATE PAPER -->

Research on leadership within anthropology extends to the birth of the discipline. Early on, anthropologists (and some sociologists) realized that leadership and followership were critical to understanding human psychology, social organization, and culture [e.g., @mumford_origins_1906; @firth1927economic; @morgan_ancient_1877; @myres_influence_1917]. Anthropologists documented some sort of leadership among every ethnographically observed society [@brown_human_1991; @lewis_leaders_1974], and across many social contexts, such as families and kin groups [@dussart2000politics], ritual [@singh_cultural_2017], work groups [@macfarlan_competitive_2012], conflicts between groups [@glowacki_evolutionary_2017], and in nonindustrial political groups [@cohen_comparative_1967]. For review, see @garfield_review_2019.

@@

Since the seminal WEIRD people paper, many social scientists have taken up the challenge to diversify their samples and have sought out "non-WEIRD" participants and databases. Dichotomizing populations and their psychologies and social dynamics as WEIRD or non-WEIRD, however, is a mistake.^[A Google Scholar search for "non-WEIRD" produced over 1000 results.] As anthropology has conclusively demonstrated, there is enormous diversity across societies that does not remotely resemble a dichotomy.

Anthropology, on the other hand, has been criticized for exoticizing and essentializing the "Other" [@said1979; @abu2008]. @abu2008 [p. 470], for instance, notes that

@@

There is as much diversity within non-Western cultures as there is within Western ones, and there is also substantial overlap of the behaviors of people everywhere [@brown_human_1991].
